The \dealii Library, Version 9.0

### 2018-04-25 9.0/paper.tex
removing last line

\paragraph*{ROL, a Rapid Optimization Library.}
  ROL \cite{ridzal2014rapid} is a package for large-scale optimization.
  \marginpar{Can we add a sentence or two about the ROL interface here?}

>>>>

\paragraph*{ROL, a Rapid Optimization Library.}
  ROL \cite{ridzal2014rapid} is a package for large-scale optimization.
  \dealii can now use the state-of-the-art algorithms in ROL to solve
  unconstrained and constrained optimization problems as well as optimization
  problems under uncertainty.
  \dealii provides an interface to ROL's (abstract) vector class using the
  adapter software pattern.
  Through such an interface any vector class in \dealii following certain
  interface requirements can be used to define a ROL objective function.
